\documentclass[a4paper,11pt]{article}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{tikz}

\definecolor{myblue}{HTML}{003366}
\hypersetup{colorlinks=true, linkcolor=myblue, urlcolor=myblue}

\titleformat{\section}{\large\bfseries\color{myblue}}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{6pt}{4pt}

\newcommand{\iconbadge}[1]{%
  \tikz[baseline=-0.55ex]{\node[circle,fill=myblue,text=white,font=\bfseries\fontsize{5}{5}\selectfont,inner sep=1.3pt,minimum size=10pt]{#1};}%
}

\title{\textbf{Akash Kothapalli --- Resume Repository Guide}}
\date{}
\author{}

\begin{document}
\maketitle

\section*{Quick Reference}

\begin{tabular}{lll}
\textbf{File} & \textbf{Output PDF} & \textbf{Target Roles} \\
\hline
\texttt{backend\_resume.tex} & \texttt{Akash\_Backend\_Developer.pdf} & Backend, Python, API Developer \\
\texttt{fullstack\_resume.tex} & \texttt{Akash\_Fullstack\_Developer.pdf} & Full Stack, Web Developer, Startup SDE \\
\texttt{software\_engineer\_resume.tex} & \texttt{Akash\_Software\_Engineer.pdf} & General SDE, Product companies \\
\end{tabular}

\section*{Header Links (all resumes)}

All three resumes use the following profile links in the header:

\begin{itemize}
\item \iconbadge{@}~Email: \href{mailto:akashkothapalli95@gmail.com}{akashkothapalli95@gmail.com}
\item \iconbadge{in}~LinkedIn: \href{https://www.linkedin.com/in/akash-techie}{linkedin.com/in/akash-techie}
\item \iconbadge{gh}~GitHub: \href{https://github.com/akash-kothapalli}{github.com/akash-kothapalli}
\item \iconbadge{lc}~LeetCode: \href{https://leetcode.com/u/Akashgeek}{leetcode.com/u/Akashgeek}
\end{itemize}

To update any profile link, search for the URL across all three \texttt{.tex} files and replace in one go.

\section*{Resume Versions}

\begin{itemize}

\item \textbf{Backend Resume} (\texttt{backend\_resume.tex})

Emphasises Python automation, PostgreSQL, Flask, REST APIs, and serverless backend work.
Apply for: Backend Developer, Python Developer, API Developer, Node.js Developer, Platform Engineer.

\item \textbf{Full Stack Resume} (\texttt{fullstack\_resume.tex})

Leads with React.js frontend skills, then backend and databases.
Apply for: Full Stack Developer, Web Developer, React + Node roles, Product engineering at startups.

\item \textbf{Software Engineer Resume} (\texttt{software\_engineer\_resume.tex})

Balanced profile emphasising system design, distributed systems, and DSA preparation.
Apply for: SDE-1 at product companies, associate engineer roles, companies running GATE/aptitude-based screening.

\end{itemize}

\section*{PDF Generation (GitHub Actions)}

PDFs are built automatically on every push to \texttt{resumes/*.tex}.

\begin{enumerate}
\item Edit any \texttt{.tex} file in the \texttt{resumes/} directory.
\item Commit and push to \texttt{main}.
\item GitHub Actions compiles all three resumes via \texttt{pdflatex}.
\item Download named PDFs from the \textbf{Actions} tab $\rightarrow$ latest workflow run $\rightarrow$ \textbf{Artifacts}.
\end{enumerate}

Output filenames: \texttt{Akash\_Backend\_Developer.pdf}, \texttt{Akash\_Fullstack\_Developer.pdf}, \texttt{Akash\_Software\_Engineer.pdf}.

\section*{What Only Changes Between Resumes}

\begin{itemize}
\item \texttt{pdftitle} in \texttt{\textbackslash hypersetup} (PDF filename metadata)
\item Profile summary paragraph
\item Skills section ordering (lead with strongest skills for that role)
\item Project description emphasis (backend API vs full-stack app vs distributed system)
\end{itemize}

Everything else --- experience bullets, education, certifications, header --- is identical.

\section*{Maintenance Rules}

\begin{itemize}
\item When adding a new project: update all three \texttt{.tex} files, adjusting the project description framing per resume type.
\item When adding new experience: add to all three, keeping bullet point language consistent with each resume's focus.
\item Never use tables, images, or multi-column layouts --- ATS systems strip them.
\item Keep each resume to exactly one page.
\end{itemize}

\end{document}
